%---------- Bijlagen ---------------------------------------------------------

\section{Code PLC}\label{sec:code_plc}

\subsection{Python script PLC} \label{sec:script_plc}
\inputminted{python3}{../tests/plc/plc-simulator.py}
\captionof{listing}{\label{listing:script_plc}Python script for PLC simulation.}
\newpage

\subsection{Dockerfile PLC} \label{sec:docker_plc}
\inputminted{python3}{../tests/plc/Dockerfile}
\captionof{listing}{\label{listing:docker_plc}Dockerfile for PLC container.}

\section{Code WCS}\label{sec:code_wcs}

\subsection{Progress 4GL script WCS} \label{sec:script_wcs}
\inputminted{python3}{../tests/wcs/wcs.p}
\captionof{listing}{\label{listing:script_wcs}Progress 4GL script for WCS.}

\section{Code Java listener}\label{sec:code_java_listener} 

\subsection{Java Listener ActiveMQ}\label{sec:listener_activemq}
\inputminted{java}{../tests/listener/activemq-listener/demo/src/main/java/com/example/ActiveMQSocketBridge.java}
\captionof{listing}{\label{listing:listener_activemq}Java Listener for ActiveMQ.}

\section{ActiveMQ}
\subsection{Configuratie}\label{sec:config_activemq}
\inputminted{java}{../tests/messaging/activemq-server/activemq.xml}
\captionof{listing}{\label{listing:configxml_activemq}config.xml for ActiveMQ.}

\inputminted{java}{../tests/messaging/activemq-server/setenv}
\captionof{listing}{\label{listing:setenv_activemq}setenv config for ActiveMQ.}

\section{RabbitMQ}
\subsection{Java Listener RabbitMQ}\label{sec:listener_rabbitmq}
\inputminted{java}{../tests/listener/rabbitmq-listener/rabbitmq-plc-listener/src/main/java/com/listener/RabbitMQSocketBridge.java}
\captionof{listing}{\label{listing:listener_rabbitmq}Java Listener for RabbitMQ.}

\subsection{Configuratie}\label{sec:config_rabbitmq}
\inputminted{python3}{../tests/messaging/rabbitmq-server/rabbitmq.conf}
\captionof{listing}{\label{listing:config_rabbitmq}Configuration file for RabbitMQ.}


\subsection{Java Listener Artemis}\label{sec:listener_artemis}
\inputminted{java}{../tests/listener/artemis-listener/demo/src/main/java/com/example/ArtemisSocketBridge.java}
\captionof{listing}{\label{listing:listener_artemis}Java Listener for Artemis.}

\section{ActiveMQ Classic test}\label{sec:code_amq}

\subsection{Dockerfile}\label{sec:docker_amq}
\inputminted{python3}{../tests/messaging/activemq-server/Dockerfile}
\captionof{listing}{\label{listing:docker_amq}Dockerfile for ActiveMQ Classic test.}

\section{RabbitMQ test}\label{sec:code_rabbitmq}

\subsection{Dockerfile}\label{sec:docker_rabbitmq}
\inputminted{python3}{../tests/messaging/rabbitmq-server/Dockerfile}
\captionof{listing}{\label{listing:docker_rabbitmq}Dockerfile for RabbitMQ server.}


\section{Artemis Classic test}\label{sec:code_artemis}

\subsection{Dockerfile}\label{sec:docker_artemis}
\inputminted{python3}{../tests/messaging/artemis-server/Dockerfile}
\captionof{listing}{\label{listing:docker_artemis}Dockerfile for Artemis Classic test.}

\subsection{Broker XML Configuration}\label{sec:broker_artemis}
\inputminted{xml}{../tests/messaging/artemis-server/broker.xml}
\captionof{listing}{\label{listing:broker_artemis}Broker XML configuration for Artemis.}

\subsection{Bootstrap XML Configuration}\label{sec:bootstrap_artemis}
\inputminted{xml}{../tests/messaging/artemis-server/bootstrap.xml}
\captionof{listing}{\label{listing:bootstrap_artemis}Bootstrap XML configuration for Artemis.}
